This document gives a proposal for a new web application, developed for 2II25, Web Technology, 2013.

\paragraph{}
We will first describe our proposed application and give some use cases for it.

\paragraph{}
Then, we will select which datasets our application will make use of, and we will show how our application uses them.

\paragraph{}
In section \ref{sec:tools} we give a list of tools we intend to use to develop this application, and a short description of how we would like to use them.
We aim to use the latest technology so we can truly make something modern.
Because of this, we choose to not have support for older environments, like old browsers not implementing modern standards.
We will also use some standards that are not fully recommended yet, such as HTML5, but we feel they have matured enough to be used comfortably.
There is always a trade-off between using new technology and losing compatibility, especially in such a short time span.
Since our application is a demonstration of our knowledge of web technology and will most likely not be used by a lot of people, we feel we can choose for the latest and greatest technologies.

\paragraph{}
We will then discuss what other data sources our application uses and how it combines them with the data we discuss in \ref{sec:datasets}.
In this section we will also show how we plan to deliver this data to our users, for instance via JSON endpoints that can be loaded into our pages using AJAX.
Our goal with respect to data is to combine data from different sources and add something of value to it, turning it into true information, in stead of merely reproducing it.
